Figures

### 2020-04-15 manuscript/appendix.Rmd
explain percentages

```{r hypsography, fig.cap = "Hypsography classification by state.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra=''}
knitr::include_graphics("../figures/01_hypsography-1.pdf")
```

>>>>

```{r hypsography, fig.cap = "Hypsography classification by state. Numbers on panel labels indicate the percentage of lakes in each state with a convex versus a concave cross-section shape.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra=''}
knitr::include_graphics("../figures/01_hypsography-1.pdf")
```
